---
title: "Bacillus growth curves"
author: "Jay T. Lennon"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{array}
output: pdf_document
geometry: margin = 2.54cm
---

# Growth curves of Bacillus subtilis: sigf::gfp vs. wildtype

# Clear workspace and set directory

```{r setup}
rm(list = ls())
knitr::opts_knit$set(root.dir=normalizePath("~/Github/SporePlaque"))
getwd()
```

## Load packages and functions

```{r}
require("png")
require("dplyr")
library("tidyverse")
require("grid")
require("tibble")
require("knitr")
require("extrafont")
require("ggrepel");
require("gridExtra")
require("contrast")
sem <- function(x) sqrt(var(x)/length(x))
cv <- function(x) (sd(x)/mean(x))*100
```

# Load data

```{r}
data <- read.csv("~/Github/SporePlaque/data/20240828_Fluor.csv")
design <- read.csv("~/Github/SporePlaque/data/20240828_OD_design.csv")
data.OD <- read.csv("~/Github/SporePlaque/data/20240828_OD.csv")
```

# Change time

```{r}
# Change times to numeric (hours)
time <- as.numeric(sub("^(\\d+):(\\d+).*", "\\1.\\2", data$Time))
```

# Create cell-specific fluorescnce data
```{r}
log.data <- log10(data[,2:ncol(data)])
trunc.od <- data.OD[,2:ncol(data.OD)]

csf.raw <- log.data %>%
  mutate(across(everything(), ~ . / trunc.od[[cur_column()]]))

csf <- data.frame(time, csf.raw)
  
  
  log.data %>%
  mutate(across(2:ncol(.), ~ . / data.OD[[cur_column()]]))

csf <- data %>%
  # Start by keeping the first column unchanged
  select(1) %>%
  # Add the division results for columns 2 through n
  bind_cols(
    data %>%
      select(-1) %>%
      mutate(across(everything(), ~ . / data.OD[[cur_column()]]))
  )
```


# Create look-up table

```{r}
# This code chunk reads in the experimental design file
# Converts 96-well plate layout into long form
# Then creates column number reference number

# Subset the design file
media <- design[1:8,1:12]
wells <- design[9:16,1:12]

# convert 96 well plate format to long format
media.long <- as.data.frame(pivot_longer(media, cols = everything(), 
              names_to = "Treatment", values_to = "Value"))
wells.long <- as.data.frame(pivot_longer(wells, cols = everything(), 
              names_to = "Treatment", values_to = "Value"))

# Create vector of column numbers
col.vect <- seq(1, 96)

# Combine into one look up table
look.table <- data.frame(media.long[,2], wells.long[,2], col.vect)
colnames(look.table) <- c("media", "well", "col")
```


# Pull out wells by treatment and make data frames

```{r}
# Following code pulls out vector of column numbers corresponding to a medium
# Then creates a data frame with time and ODs
# Need to add one (+1) because of how time in read in
# Note: there are some wells with no growth that could be removed here

# Minus cells
nocell.LB.full.wt.col <- look.table %>%
  filter(media == "LB.full.dead.wt") %>%
  pull(col)
nocell.LB.full.wt <- data.frame(time, data[, nocell.LB.full.wt.col+1])
colnames(nocell.LB.full.wt)[1] <- "time"

nocell.LB.full.sigf.col <- look.table %>%
  filter(media == "LB.full.dead.sigf") %>%
  pull(col)
nocell.LB.full.sigf <- data.frame(time, data[, nocell.LB.full.sigf.col+1])
colnames(nocell.LB.full.sigf)[1] <- "time"

nocell.LB.dil.wt.col <- look.table %>%
  filter(media == "LB.dil.dead.wt") %>%
  pull(col)
nocell.LB.dil.wt <- data.frame(time, data[, nocell.LB.dil.wt.col+1])
colnames(nocell.LB.dil.wt)[1] <- "time"

nocell.LB.dil.sigf.col <- look.table %>%
  filter(media == "LB.dil.dead.sigf") %>%
  pull(col)
nocell.LB.dil.sigf <- data.frame(time, data[, nocell.LB.dil.sigf.col+1])
colnames(nocell.LB.dil.sigf)[1] <- "time"

nocell.DSM.full.wt.col <- look.table %>%
  filter(media == "DSM.full.dead.wt") %>%
  pull(col)
nocell.DSM.full.wt <- data.frame(time, data[, nocell.DSM.full.wt.col+1])
colnames(nocell.DSM.full.wt)[1] <- "time"

nocell.DSM.full.sigf.col <- look.table %>%
  filter(media == "DSM.full.dead.sigf") %>%
  pull(col)
nocell.DSM.full.sigf <- data.frame(time, data[, nocell.DSM.full.sigf.col+1])
colnames(nocell.DSM.full.sigf)[1] <- "time"

nocell.DSM.dil.wt.col <- look.table %>%
  filter(media == "DSM.dil.dead.wt") %>%
  pull(col)
nocell.DSM.dil.wt <- data.frame(time, data[, nocell.DSM.dil.wt.col+1])
colnames(nocell.CDSM.dil.wt)[1] <- "time"

nocell.DSM.dil.sigf.col <- look.table %>%
  filter(media == "DSM.dil.dead.sigf") %>%
  pull(col)
nocell.DSM.dil.sigf <- data.frame(time, data[, nocell.DSM.dil.sigf.col+1])
colnames(nocell.DSM.dil.sigf)[1] <- "time"

nocell.CDSM.full.wt.col <- look.table %>%
  filter(media == "CDSM.full.dead.wt") %>%
  pull(col)
nocell.CDSM.full.wt <- data.frame(time, data[, nocell.CDSM.full.wt.col+1])
colnames(nocell.CDSM.full.wt)[1] <- "time"

nocell.CDSM.full.sigf.col <- look.table %>%
  filter(media == "CDSM.full.dead.sigf") %>%
  pull(col)
nocell.CDSM.full.sigf <- data.frame(time, data[, nocell.CDSM.full.sigf.col+1])
colnames(nocell.CDSM.full.sigf)[1] <- "time"

nocell.CDSM.dil.wt.col <- look.table %>%
  filter(media == "CDSM.dil.dead.wt") %>%
  pull(col)
nocell.CDSM.dil.wt <- data.frame(time, data[, nocell.CDSM.dil.wt.col+1])
colnames(nocell.CDSM.dil.wt)[1] <- "time"

nocell.CDSM.dil.sigf.col <- look.table %>%
  filter(media == "CDSM.dil.dead.sigf") %>%
  pull(col)
nocell.CDSM.dil.sigf <- data.frame(time, data[, nocell.CDSM.dil.sigf.col+1])
colnames(nocell.CDSM.dil.sigf)[1] <- "time"


# Plus cells
cell.LB.full.wt.col <- look.table %>%
  filter(media == "LB.full.live.wt") %>%
  pull(col)
cell.LB.full.wt <- data.frame(time, data[, cell.LB.full.wt.col+1])
colnames(cell.LB.full.wt)[1] <- "time"

cell.LB.full.sigf.col <- look.table %>%
  filter(media == "LB.full.live.sigf") %>%
  pull(col)
cell.LB.full.sigf <- data.frame(time, data[, cell.LB.full.sigf.col+1])
colnames(cell.LB.full.sigf)[1] <- "time"

cell.LB.dil.wt.col <- look.table %>%
  filter(media == "LB.dil.live.wt") %>%
  pull(col)
cell.LB.dil.wt <- data.frame(time, data[, cell.LB.dil.wt.col+1])
colnames(cell.LB.dil.wt)[1] <- "time"

cell.LB.dil.sigf.col <- look.table %>%
  filter(media == "LB.dil.live.sigf") %>%
  pull(col)
cell.LB.dil.sigf <- data.frame(time, data[, cell.LB.dil.sigf.col+1])
colnames(cell.LB.dil.sigf)[1] <- "time"

cell.DSM.full.wt.col <- look.table %>%
  filter(media == "DSM.full.live.wt") %>%
  pull(col)
cell.DSM.full.wt <- data.frame(time, data[, cell.DSM.full.wt.col+1])
colnames(cell.DSM.full.wt)[1] <- "time"

cell.DSM.full.sigf.col <- look.table %>%
  filter(media == "DSM.full.live.sigf") %>%
  pull(col)
cell.DSM.full.sigf <- data.frame(time, data[, cell.DSM.full.sigf.col+1])
colnames(cell.DSM.full.sigf)[1] <- "time"

cell.DSM.dil.wt.col <- look.table %>%
  filter(media == "DSM.dil.live.wt") %>%
  pull(col)
cell.DSM.dil.wt <- data.frame(time, data[, cell.DSM.dil.wt.col+1])
colnames(cell.DSM.dil.wt)[1] <- "time"

cell.DSM.dil.sigf.col <- look.table %>%
  filter(media == "DSM.dil.live.sigf") %>%
  pull(col)
cell.DSM.dil.sigf <- data.frame(time, data[, cell.DSM.dil.sigf.col+1])
colnames(cell.DSM.dil.sigf)[1] <- "time"

cell.CDSM.full.wt.col <- look.table %>%
  filter(media == "CDSM.full.live.wt") %>%
  pull(col)
cell.CDSM.full.wt <- data.frame(time, data[, cell.CDSM.full.wt.col+1])
colnames(cell.CDSM.full.wt)[1] <- "time"

cell.CDSM.full.sigf.col <- look.table %>%
  filter(media == "CDSM.full.live.sigf") %>%
  pull(col)
cell.CDSM.full.sigf <- data.frame(time, data[, cell.CDSM.full.sigf.col+1])
colnames(cell.CDSM.full.sigf)[1] <- "time"

cell.CDSM.dil.wt.col <- look.table %>%
  filter(media == "CDSM.dil.live.wt") %>%
  pull(col)
cell.CDSM.dil.wt <- data.frame(time, data[, cell.CDSM.dil.wt.col+1])
colnames(cell.CDSM.dil.wt)[1] <- "time"

cell.CDSM.dil.sigf.col <- look.table %>%
  filter(media == "CDSM.dil.live.sigf") %>%
  pull(col)
cell.CDSM.dil.sigf <- data.frame(time, data[, cell.CDSM.dil.sigf.col+1])
colnames(cell.CDSM.dil.sigf)[1] <- "time"
```


# Make no-cell figure

```{r}

# Following line initiate location to write file
png(filename ="~/Github/SporePlaque/figures/20240828_nocell.png", 
    width = 800, height = 1200, res = 96 * 2) 

# Start plot 
plot.new()

# Define plotting margins
#par(mar = c(7, 7, 5, 7))
#par(mfrow = c(3, 1))
#par(mfrow = c(3, 1), mar = c(5, 5, 3, 5))
par(mfrow = c(3, 1), mar = c(4, 8, 1, 8), oma = c(0, 0, 0, 0))

# Plot 1 - LB medium

# Make plot full strength LB (wt) no cells
plot(nocell.LB.full.wt[,1], nocell.LB.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 40000), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(nocell.LB.full.wt)) {
  lines(nocell.LB.full.wt[,1], nocell.LB.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength LB (sigf) no cells
for(i in 2:ncol(nocell.LB.full.sigf)) {
  lines(nocell.LB.full.sigf[,1], nocell.LB.full.sigf[,i], col = "grey", lty = 1)  
}

# Add diluted LB (wt) no cells
for(i in 2:ncol(nocell.LB.dil.wt)) {
  lines(nocell.LB.dil.wt[,1], nocell.LB.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted LB (sigf) no cells
for(i in 2:ncol(nocell.LB.dil.sigf)) {
  lines(nocell.LB.dil.sigf[,1], nocell.LB.dil.sigf[,i], col = "grey", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10000", "20000", "30000"), at = c(0, 10000, 20000, 30000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10000, 20000, 30000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("LB (full)", "LB (diluted)"), 
       col = c("grey", "grey"), lty = c(1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 2 - DSM medium

# Make plot full strength DSM (wt) no cells
plot(nocell.DSM.full.wt[,1], nocell.DSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 40000), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(nocell.DSM.full.wt)) {
  lines(nocell.DSM.full.wt[,1], nocell.DSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength DSM (sigf) no cells
for(i in 2:ncol(nocell.DSM.full.sigf)) {
  lines(nocell.DSM.full.sigf[,1], nocell.DSM.full.sigf[,i], col = "grey", lty = 1)  
}

# Add diluted DSM (wt) no cells
for(i in 2:ncol(nocell.DSM.dil.wt)) {
  lines(nocell.DSM.dil.wt[,1], nocell.DSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted DSM (sigf) no cells
for(i in 2:ncol(nocell.DSM.dil.sigf)) {
  lines(nocell.DSM.dil.sigf[,1], nocell.DSM.dil.sigf[,i], col = "grey", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10000", "20000", "30000"), at = c(0, 10000, 20000, 30000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10000, 20000, 30000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("DSM (full)", "DSM (diluted)"), 
       col = c("grey", "grey"), lty = c(1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 3 - CDSM medium

# Make plot full strength DSM (wt) no cells
plot(nocell.CDSM.full.wt[,1], nocell.CDSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 1000), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(nocell.CDSM.full.wt)) {
  lines(nocell.CDSM.full.wt[,1], nocell.CDSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength DSM (sigf) no cells
for(i in 2:ncol(nocell.CDSM.full.sigf)) {
  lines(nocell.CDSM.full.sigf[,1], nocell.CDSM.full.sigf[,i], col = "grey", lty = 1)  
}

# Add diluted DSM (wt) no cells
for(i in 2:ncol(nocell.CDSM.dil.wt)) {
  lines(nocell.CDSM.dil.wt[,1], nocell.CDSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted CDSM (sigf) no cells
for(i in 2:ncol(nocell.CDSM.dil.sigf)) {
  lines(nocell.CDSM.dil.sigf[,1], nocell.CDSM.dil.sigf[,i], col = "grey", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "500", "1000"), at = c(0, 500, 1000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 500, 1000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
    labels = c("0", "12", "24"), at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
      line = -1, adj = 0.5)

# Add a legend
legend("topleft", legend = c("CDSM (full)", "CDSM (diluted)"), 
       col = c("grey", "grey"), lty = c(1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Close plot device (completes writing of file)
dev.off()
graphics.off()

# Shows plot in R console window
img <- readPNG("~/Github/SporePlaque/figures/20240828_nocell.png")
grid.raster(img)
```


# Make plus-cell figure

```{r}

# Following line initiate location to write file
png(filename ="~/Github/SporePlaque/figures/20240828_pluscell.png", 
    width = 800, height = 1200, res = 96 * 2) 

# Start plot 
plot.new()

# Define plotting margins
#par(mar = c(7, 7, 5, 7))
#par(mfrow = c(3, 1))
#par(mfrow = c(3, 1), mar = c(5, 5, 3, 5))
par(mfrow = c(3, 1), mar = c(4, 8, 1, 8), oma = c(0, 0, 0, 0))

# Plot 1 - LB medium

# Make plot full strength LB (wt) cells
plot(cell.LB.full.wt[,1], cell.LB.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 40000), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(cell.LB.full.wt)) {
  lines(cell.LB.full.wt[,1], cell.LB.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength LB (sigf) cells
for(i in 2:ncol(cell.LB.full.sigf)) {
  lines(cell.LB.full.sigf[,1], cell.LB.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted LB (wt) cells
for(i in 2:ncol(cell.LB.dil.wt)) {
  lines(cell.LB.dil.wt[,1], cell.LB.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted LB (sigf) cells
for(i in 2:ncol(cell.LB.dil.sigf)) {
  lines(cell.LB.dil.sigf[,1], cell.LB.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10000", "20000", "30000"), at = c(0, 10000, 20000, 30000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10000, 20000, 30000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("LB (full)", "LB (diluted)", "LB (full)", "LB (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 2 - DSM medium

# Make plot full strength DSM (wt) cells
plot(cell.DSM.full.wt[,1], cell.DSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 40000), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(cell.DSM.full.wt)) {
  lines(cell.DSM.full.wt[,1], cell.DSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength DSM (sigf)  cells
for(i in 2:ncol(cell.DSM.full.sigf)) {
  lines(cell.DSM.full.sigf[,1], cell.DSM.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted DSM (wt) cells
for(i in 2:ncol(cell.DSM.dil.wt)) {
  lines(cell.DSM.dil.wt[,1], cell.DSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted DSM (sigf) no cells
for(i in 2:ncol(cell.DSM.dil.sigf)) {
  lines(cell.DSM.dil.sigf[,1], cell.DSM.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10000", "20000", "30000"), at = c(0, 10000, 20000, 30000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10000, 20000, 30000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("DSM (full)", "DSM (diluted)", "DSM (full)", "DSM (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 3 - CDSM medium

# Make plot full strength DSM (wt) cells
plot(cell.CDSM.full.wt[,1], cell.CDSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 2500), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(cell.CDSM.full.wt)) {
  lines(cell.CDSM.full.wt[,1], cell.CDSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength DSM (sigf) cells
for(i in 2:ncol(cell.CDSM.full.sigf)) {
  lines(cell.CDSM.full.sigf[,1], cell.CDSM.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted DSM (wt)  cells
for(i in 2:ncol(cell.CDSM.dil.wt)) {
  lines(cell.CDSM.dil.wt[,1], cell.CDSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted CDSM (sigf) cells
for(i in 2:ncol(cell.CDSM.dil.sigf)) {
  lines(cell.CDSM.dil.sigf[,1], cell.CDSM.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "1000", "2000"), at = c(0, 1000, 2000))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 1000, 2000))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
    labels = c("0", "12", "24"), at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Fluorescence (RFU)', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
      line = -1, adj = 0.5)

# Add a legend
legend("topleft", legend = c("CDSM (full)", "CDSM (diluted)", "CDSM (full)", "CDSM (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Close plot device (completes writing of file)
dev.off()
graphics.off()

# Shows plot in R console window
img <- readPNG("~/Github/SporePlaque/figures/20240828_pluscell.png")
grid.raster(img)
```


### Cell-specific fluorescence

```{r}
# Plus cells
csf.LB.full.wt.col <- look.table %>%
  filter(media == "LB.full.live.wt") %>%
  pull(col)
csf.LB.full.wt <- data.frame(time, csf[, cell.LB.full.wt.col+1])
colnames(csf.LB.full.wt)[1] <- "time"

csf.LB.full.sigf.col <- look.table %>%
  filter(media == "LB.full.live.sigf") %>%
  pull(col)
csf.LB.full.sigf <- data.frame(time, csf[, cell.LB.full.sigf.col+1])
colnames(csf.LB.full.sigf)[1] <- "time"

csf.LB.dil.wt.col <- look.table %>%
  filter(media == "LB.dil.live.wt") %>%
  pull(col)
csf.LB.dil.wt <- data.frame(time, csf[, cell.LB.dil.wt.col+1])
colnames(csf.LB.dil.wt)[1] <- "time"

csf.LB.dil.sigf.col <- look.table %>%
  filter(media == "LB.dil.live.sigf") %>%
  pull(col)
csf.LB.dil.sigf <- data.frame(time, csf[, cell.LB.dil.sigf.col+1])
colnames(csf.LB.dil.sigf)[1] <- "time"

csf.DSM.full.wt.col <- look.table %>%
  filter(media == "DSM.full.live.wt") %>%
  pull(col)
csf.DSM.full.wt <- data.frame(time, csf[, cell.DSM.full.wt.col+1])
colnames(csf.DSM.full.wt)[1] <- "time"

csf.DSM.full.sigf.col <- look.table %>%
  filter(media == "DSM.full.live.sigf") %>%
  pull(col)
csf.DSM.full.sigf <- data.frame(time, csf[, cell.DSM.full.sigf.col+1])
colnames(csf.DSM.full.sigf)[1] <- "time"

csf.DSM.dil.wt.col <- look.table %>%
  filter(media == "DSM.dil.live.wt") %>%
  pull(col)
csf.DSM.dil.wt <- data.frame(time, csf[, cell.DSM.dil.wt.col+1])
colnames(csf.DSM.dil.wt)[1] <- "time"

csf.DSM.dil.sigf.col <- look.table %>%
  filter(media == "DSM.dil.live.sigf") %>%
  pull(col)
csf.DSM.dil.sigf <- data.frame(time, csf[, cell.DSM.dil.sigf.col+1])
colnames(csf.DSM.dil.sigf)[1] <- "time"

csf.CDSM.full.wt.col <- look.table %>%
  filter(media == "CDSM.full.live.wt") %>%
  pull(col)
csf.CDSM.full.wt <- data.frame(time, csf[, cell.CDSM.full.wt.col+1])
colnames(csf.CDSM.full.wt)[1] <- "time"

csf.CDSM.full.sigf.col <- look.table %>%
  filter(media == "CDSM.full.live.sigf") %>%
  pull(col)
csf.CDSM.full.sigf <- data.frame(time, csf[, cell.CDSM.full.sigf.col+1])
colnames(csf.CDSM.full.sigf)[1] <- "time"

csf.CDSM.dil.wt.col <- look.table %>%
  filter(media == "CDSM.dil.live.wt") %>%
  pull(col)
csf.CDSM.dil.wt <- data.frame(time, csf[, cell.CDSM.dil.wt.col+1])
colnames(csf.CDSM.dil.wt)[1] <- "time"

csf.CDSM.dil.sigf.col <- look.table %>%
  filter(media == "CDSM.dil.live.sigf") %>%
  pull(col)
csf.CDSM.dil.sigf <- data.frame(time, csf[, cell.CDSM.dil.sigf.col+1])
colnames(csf.CDSM.dil.sigf)[1] <- "time"
```


# Make cell-specific fluorescence figure
```{r}
# Following line initiate location to write file
png(filename ="~/Github/SporePlaque/figures/20240828_csf.png", 
    width = 800, height = 1200, res = 96 * 2) 

# Start plot 
plot.new()

# Define plotting margins
#par(mar = c(7, 7, 5, 7))
#par(mfrow = c(3, 1))
#par(mfrow = c(3, 1), mar = c(5, 5, 3, 5))
par(mfrow = c(3, 1), mar = c(4, 8, 1, 8), oma = c(0, 0, 0, 0))

# Plot 1 - LB medium

# Make plot full strength LB (wt) cells
plot(csf.LB.full.wt[,1], csf.LB.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 20), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(cell.LB.full.wt)) {
  lines(csf.LB.full.wt[,1], csf.LB.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength LB (sigf) cells
for(i in 2:ncol(csf.LB.full.sigf)) {
  lines(csf.LB.full.sigf[,1], csf.LB.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted LB (wt) cells
for(i in 2:ncol(cell.LB.dil.wt)) {
  lines(csf.LB.dil.wt[,1], csf.LB.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted LB (sigf) cells
for(i in 2:ncol(csf.LB.dil.sigf)) {
  lines(csf.LB.dil.sigf[,1], csf.LB.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10", "20"), at = c(0, 10, 20))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10, 20))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Cell-specific fluorescence', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("LB (full)", "LB (diluted)", "LB (full)", "LB (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 2 - DSM medium

# Make plot full strength DSM (wt) cells
plot(csf.DSM.full.wt[,1], csf.DSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 20), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(csf.DSM.full.wt)) {
  lines(csf.DSM.full.wt[,1], csf.DSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength DSM (sigf)  cells
for(i in 2:ncol(csf.DSM.full.sigf)) {
  lines(csf.DSM.full.sigf[,1], csf.DSM.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted DSM (wt) cells
for(i in 2:ncol(csf.DSM.dil.wt)) {
  lines(csf.DSM.dil.wt[,1], csf.DSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted DSM (sigf) cells
for(i in 2:ncol(csf.DSM.dil.sigf)) {
  lines(csf.DSM.dil.sigf[,1], csf.DSM.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10", "20"), at = c(0, 10, 20))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 10, 20))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
#    labels = c("0", "12", "24"), at = c(0, 12, 24))
     labels = F, at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Cell-specific fluorescence', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

#mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
#      line = -4, adj = 0.5)

# Add a legend
legend("topleft", legend = c("DSM (full)", "DSM (diluted)", "DSM (full)", "DSM (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Plot 3 - CDSM medium

# Make plot full strength DSM (wt) cells
plot(csf.CDSM.full.wt[,1], csf.CDSM.full.wt[,2], xlim = c(-1, 25), 
     ylim = c(0, 20), type = "l", 
     lty = 1, col = "grey", lwd = 2, ylab = "", xlab = "", 
     cex.lab = 1.5, las = 1, yaxt = "n", xaxt = "n")

# Add lines for other replicates (color = grey)
# We just plotted column 2 and 1
# Now we plot column 3 and 1, and so forth
for(i in 3:ncol(csf.CDSM.full.wt)) {
  lines(csf.CDSM.full.wt[,1], csf.CDSM.full.wt[,i], col = "grey", lty = 1)  
}

# Add full strength CDSM (sigf) cells
for(i in 2:ncol(csf.CDSM.full.sigf)) {
  lines(csf.CDSM.full.sigf[,1], csf.CDSM.full.sigf[,i], col = "green", lty = 1)  
}

# Add diluted CDSM (wt)  cells
for(i in 2:ncol(csf.CDSM.dil.wt)) {
  lines(csf.CDSM.dil.wt[,1], csf.CDSM.dil.wt[,i], col = "grey", lty = 2)  
}

# Add diluted CDSM (sigf) cells
for(i in 2:ncol(csf.CDSM.dil.sigf)) {
  lines(csf.CDSM.dil.sigf[,1], csf.CDSM.dil.sigf[,i], col = "green", lty = 2)  
}

# Add box around plot
box(lwd = 2)

# Add axis ticks and labels
axis(side = 2, lwd.ticks = 2, las = 1, cex.axis = 1.25, 
     labels = c("0", "10", "20"), at = c(0, 10, 20))

axis(side = 4, labels = F, lwd.ticks = 2, at = c(0, 25,50))

axis(side = 1, lwd.ticks = 2, cex.axis = 1.25, las = 1, mgp = c(1, 1, 0),
    labels = c("0", "12", "24"), at = c(0, 12, 24))

axis(side = 3, labels = F, lwd.ticks = 2, las = 1, cex.axis = 1, 
   at = c(0, 12, 24))

# Add axis labels
mtext('Cell-specific fluorescence', side = 2, outer = TRUE, cex = 1.5, 
      line = -2.5, adj = 0.6)

mtext('Time (h)', side = 1, outer = TRUE, cex = 1.5, 
      line = -1, adj = 0.5)

# Add a legend
legend("topleft", legend = c("CDSM (full)", "CDSM (diluted)", "CDSM (full)", "CDSM (diluted)"), 
       col = c("grey", "grey", "green", "green"), lty = c(1, 2, 1, 2), 
       cex = 1, bty = "n", bg = "transparent", seg.len = 1)

# Close plot device (completes writing of file)
dev.off()
graphics.off()

# Shows plot in R console window
img <- readPNG("~/Github/SporePlaque/figures/20240828_csf.png")
grid.raster(img)
```